Databrary: Enabling sharing and reuse of research video

### 2015-04-16 jcdl-15/demo.tex
Minor edits, fix typos

Focusing on a particular research domain allows us to develop tools informed by how the intended community of users currently works, while accommodating the specific privacy concerns for data that often has a high disclosure risk.
We have created a set of data management features that empower researchers to actively manage their own projects---to upload data with accompanying metadata---as each study unfolds. 
These features include a spreadsheet interface for entering, editing, and viewing the metadata for all sessions related to a study. Session-level metadata might participant details, conditions of study, tasks in the experiment, permission levels, study groups and conditions, and serves the purpose of providing ways to browse and search for specific video data in Databrary. 
We have found that most researchers use desktop spreadsheets for managind data in their own labs, making the interface and functionality intuitive to users. 
We have also implemented a timeline for uploading, viewing, and tagging video assets related to sessions.
The timeline view is designed to look and operate like video editing software commonly used in many research labs.
A common practice for researchers in this domain who make use of video data is to have multiple, parallel camera views, or a sequence of recordings documenting the same study session.
The timeline view then allows users to upload video files, position them to reflect the temporal order of each video collected, and annotate video sections with user-generated tags.

>>>>

Focusing on a particular research domain allows us to develop tools informed by how the intended community of users currently works, while accommodating the specific privacy concerns for data that often has a high disclosure risk.
We have created a set of data management features that empower researchers to actively manage their own projects---to upload data with accompanying metadata---as each study unfolds. 
These features include a spreadsheet interface for entering, editing, and viewing the metadata for all sessions related to a study.
Session-level metadata might include participant details, conditions of study, tasks in the experiment, permission levels, study groups, or conditions, and serves the purpose of providing ways to browse and search for specific video data in Databrary. 
We have found that most researchers use desktop spreadsheets for managing data in their own labs, making the interface and functionality intuitive to users.

We have also implemented a timeline for uploading, viewing, and tagging video assets related to sessions.
The timeline view is designed to look and operate like video editing software commonly used in many research labs.
A common practice for researchers in this domain who make use of video data is to have multiple, parallel camera views, or a sequence of recordings documenting the same study session.
The timeline view then allows users to upload video files, position them to reflect the temporal order of each video collected, and annotate video sections with user-generated tags.
